% !TEX root = ../main.tex

\section{Managing with a Password}

\cf online banking (cormac herley).

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =

\subsection{Password-Derived Key} 
Also known as deterministic wallet, is a system that derives the keys from a starting point known as seed that could be random or user chosen string. This is good in the security manner that there is no need to save the private keys in a computer and just save the string or write it down on a paper. There are different methods to secure this technique such as high iteration counts to slow down the attacker on simple user-chosen strings. It is important to use a strong string as it would be the key to access the funds, services such as brainwallet \footnote{\url{http://brainwallet.org/}} make this technique available to users. Even though the keys are not stored in the computer and are resistant to physical theft, this technique is not malware resistant as a simple key logger could make the funds available to the attacker so does the physical observation. Depending on the key generation method, the most common methods are open source and also could be done in offline systems so no trust in third party is needed. However if the user forgets his keys the funds are lost forever as there is no way to recover the private keys without the initial seed, also for a new key the whole process should be repeated. One problem with this technique is that it is highly dependent on the software it use to generate the keys from the initial string and if the software is not available it would be hard to reproduce the keys from the string. That being said, as long as the software is available the funds are accessible from any computer that has access to the software. 

\begin{itemize}
  \item entropy reduction
  \item salt, iteration count
  \item parsing (spec that was followed) requires a tool. if you lose the tool, you may not be able to recover your keys. standard may not be detailed enough, or not properly implemented.
  \item change accounts gets messy
\end{itemize}

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =

\subsection{Hosted (Hot Storage)} 
One easier way to manage your bitcoin wallet is by using online wallets. It has it's own advantages and cutbacks. Trusting third party is one issue and the party getting hacked is another. There has been known trustable third parties that just went out of business on their first big hacks, such as instawallet\footnote{\url{http://www.theverge.com/2013/4/3/4180020/bitcoin-service-instawallet-suspended-indefinitely-after-hack}}, Bitcoinica\footnote{\url{http://www.theverge.com/2012/8/10/3233711/second-bitcoin-lawsuit-is-filed-in-california}}, etc. Bitcoinica in 2012 lost more than 60,000 bitcoins due to two successful attacks.\\
In the time of writing this paper the most popular online wallet is blockchain.info\footnote{\url{https://blockchain.info/wallet}} that offers two-factor authentication via email verification, but resistant to forgetting the password.\\ These online services might shutdown due to legal implications or attacks, Also the user might be tricked to reveal his password on a phishing attack\footnote{\url{http://www.theverge.com/2013/4/5/4186808/bitcoin-banker-coinbase-phishing-attacks-user-information-leaked}}, thus these services are not resistant to physical observation.
In short, Hosted (Hot) wallets are not malware resistant nor keep the keys offline, also there is the need of trust and also it is not resistant to physical theft, however because of the usual backup of such services it is resilient to equipment failure. They might offer password reset options to recover the lost password. Compatibility with change keys is as easy as doing a transaction to the new account and they offer immediate access to the funds as they are online services and synced with block chain and usually accessible through a browser thus portable and no need for a new software.

% = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = = =

\subsection{Hosted (Cold Storage)} 
It is possible to apply the offline storage method to hosted wallets but there are more drawbacks than benefits, not assuming security as the only measure. coinbase announced that more than 87\% of it's users bitcoins are stored in cold storage\footnote{\url {http://blog.coinbase.com/post/33197656699/coinbase-now-storing-87-of-customer-funds-offline}}. It would be secure for most uses but if the total withdrawal in a period of time becomes greater than the funds available in online storage there would be a 48 hours delay on the payments, for scoring purpose we assume this service is fully implemented in cold storage and there is no bitcoins in hot storage of the service.
With keys being offline, it would have resistance toward malwares but no immediate access to the funds, however the user should trust the third party service. The rest of the benefits are the same as hosted on online storage.

%\begin{itemize}
%  \item Offline wallets aka cold storage. not immediately available, transactions queueing up (coinbase). 
% \end{itemize}

